---
title: 'Awesome title'
subtitle: "subtitle"  
author: "<span style = 'font-size: 90%;'>Nicholas Tierney, Monash University</span>"
date: "<span style = 'font-size: 90%;'>CONFERENCE <br><br> MONDAY 1st January, 1920 </span> <br><br> `r #icon::fa('link')` [LINK]() <br><br>`r #icon::fa('twitter')` [nj_tierney](https://twitter.com/nj_tierney)"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: [njtheme.css, extra.css, animate.css]
    nature:
      ratio: "16:9"
      titleSlideClass: ["left", "middle", "inverse"]
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

layout: true
<div class="my-footer"><span>bit.ly/LINK • @nj_tierney</span></div> 

```{r setup, include=FALSE}
# options(htmltools.dir.version = FALSE, width = 120)
# NOTE TO SELF: The CSS styles were created in `create-njt-theme.R`
knitr::opts_chunk$set(
  fig.path = "figures/",
  cache.path = "cache/",
  fig.align = "center",
  fig.width = 13,
  fig.height = 6,
  fig.retina = 3,
  fig.show = "hold",
  external = TRUE,
  # dev = "svglite",
  # dev.args = list(bg = "transparent"),
  message = FALSE,
  warning = FALSE,
  cache = FALSE,
  echo = FALSE,
  autodep = TRUE
)
```

```{r library, include = FALSE}
library(tidyverse)
library(visdat)
library(naniar)
library(gganimate)
library(knitr)
library(ggrepel)
```



```{r helpers, include=FALSE}
mp4_vid <- function(src){
  HTML(
    paste0(
      '<video autoplay>
        <source src="', src, '" type="video/mp4">
      </video>'
    )
  )
}

fig.fullsize <- c(fig.height = 3.5, fig.width = 8, out.width = "150%"
)

as_table <- function(...) knitr::kable(..., format='html', digits = 3)

theme_set(
  theme_grey(base_size = 16) +
  theme(
    legend.position = "bottom",
    plot.background = element_rect(fill = "transparent"),
    legend.background = element_rect(fill = "transparent")
  )
)

# **ni**ck's **pa**lette
nipa <- list(red = "#c03018",
             orange = "#f0a800",
             green = "#609048",
             purple = "#484878",
             light_purple = "#A3A3BB",
             light_green = "#AFC7A3",
             light_orange = "#F7D37F",
             light_red = "#DF978B",
             pale_purple = "#ECECF1",
             pale_green = "#D7E3D1",
             pale_orange = "#FBE9BF",
             pale_red = "#EFCBC4")

```

---
class: inverse, middle, center

# Intro

---

# Background

---

Put More slides here.

---

# Take homes

---

# Future Directions

.large[
- More features
- More features
- More features
]

---

# Test

.small[small]
.

---

# Thanks

.large.pull-left[
- So many great people
- So many great people
- So many great people
- So many great people
]

.large.pull-right[
- So many great people
- So many great people
- So many great people
- So many great people
]

---

# Resources

.large[
- So many things
- So many things
- So many things
- So many things
]

---

# Colophon

.large[
- Slides made using [xaringan](https://github.com/yihui/xaringan)
- Extended with [xaringanthemer](https://github.com/gadenbuie/xaringanthemer)
- Colours taken + modified from [lorikeet theme from ochRe](https://github.com/ropenscilabs/ochRe)
- Header font is **Josefin Sans**
- Body text font is **Montserrat**
- Code font is **Fira Mono**
- template available: [njtierney/njt-talks](github.com/njtierney/njt-talks)
]

---

# Learning more

.large[
`r icon::fa_box_open() ` [package link]()

`r icon::fa('link')` [talk link]()

`r icon::fa_twitter()` nj_tierney

`r icon::fa_github()` njtierney

`r icon::fa_paper_plane()` nicholas.tierney@gmail.com

]


---

.vhuge[
**End.**
]
